---
title: "linear model from Web"
author: "Karina Toribio"
date: "Put semester and year"
output:
   html_document:
         toc: true 
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction 
We predict a simulated strength score based on arm and grip strength. We will find 3 different models and compare them. The response variable is numerical and the explanatory variable is numerical, meaning that we are using the num~num helper file.

## Model 1 SIM~ARMS

## Results

### Graphical Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

This graph is showing that as the arm strength increases, the simulation follows.

### Numerical Results 

```{r}
cor(SIMS~ARM,data=data)
```

The correlation is 0.69 which is showing that arm strength is related to sim score.

### Inferential Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

We reject the null hypothesis, both the intercept and the coefficient of ARM strength are significantly different from 0.

### Prediction Interval 

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score 

## Model 2 SIM~GRIP

## Results

### Graphical Results 
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```

As the grip strength increases the sim increases. The spread of the points around the regression line  on the grip plot are more spread out than the arm strength plot.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation is ).64, which shows that the grip strength is related to simulated strength score.

### Inferential Results
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

Based on the results, I reject the null hypothesis because the p-value is  too small as shown in the numbers above.


#### Prediction Interval

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```

The 95% prediction interval is from -3.1 to 2.0

#### now add the model fit to our plot for model.2

## Model 3 SIM~ARM+GRIP

## Results 

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation is 0. which is showing that arm strength is related to sim score.

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

As arm + grip strength goes up the simulation indicates that the sim goes up as well, we reject the null hypothesis because the p-value is so small.Both coefficients are significant.

#### Prediction Interval

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```

The prediction interval is from 0.15 to -2.13 for sim score 

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova(model.3,model.1)
```
The p-value is .00000499, concluding that I reject the null hypothesis. Model 1 is better than model 2 because the RSS for model 1 is smaller than model 2. 

```{r}
anova(model.3,model.2)
```

The p-value is . , concluding that I reject the null hypothesis. Model 3 is smaller than model 2 because the RSS for model 3 is smaller than model 2.

# Discussion and Conclusion 

All in all, model 3 is the best because it has a smaller RSS than both model 1 and model 2. Model 1 is better than model 2, but in order for it to be better, it would need a smaller RSS. In the end, we are rejecting the null hypothesis and model 3 is the best overall.


